Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
Fix compiler section.

\section{Compiler}
\label{sec:compiler}
\[
\comp{\cdot} : \src{i}^* \fun \com{i}^*
\]
\dominique{27-09-2017: Regarding the type signature for $[\cdot]$ above: does this mean that it maps lists of instructions to lists of instructions? Is there another function that compiles a single instruction to a list of instructions?}
\lau{28-09-2017: Yes, that was the thought at the moment, but this may very well change soon. This compiler would then use a compiler that compiles single instructions. That said, this part was added a long time ago and for some reason (some details about the compilation probably did not make sense to me at the moment), I did not complete it. I think the compiler will probably change to be from programs to programs, and a programs is not just going to be a list of instructions.}

\[
  \comp{\scall{\offpc,\offsigma}{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

\clearpage

>>>>

\section{Compiler}
\label{sec:compiler}

The compiler is the identity.
